Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
New image for malacology implementation
Minor rewording to 3.1

\paragraph*{Malacology:} Malacology exposes Ceph's PAXOS-based monitoring
service by embedding a Lua VM in the monitors that implements a generic API
for creating dynamic interfaces around existing subsystems that may associated
additional state with a subsystem map.
As a consequence of this, applications can define simple but useful 
domain-specific logic to the PAXOS quorum, such as authorization control (just 
specific clients can write new values) or to trigger actions based on specific 
values (e.g. sanitize values). Since the monitor is intended to be out of 
high-performance I/O paths, a general guideline is to make use of this 
functionality infrequently and to assign small values to maps. Malacology itself 
makes use of this functionality to version object interfaces defined in OSDs 
(\S\ref{active-storage}) and load balancing policies in MDSs 
(\S\ref{malacology:mds}).

@@

\begin{figure}[htbp]
\centering
\includegraphics{figures/implementation.png}
\caption{Malacology re-uses Ceph subsystems to manage interface classes.
After the proposal is accepted by the cluster of monitors, the
script is redundantly and consistently distributed to OSDs.
\label{fig:implementation}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{figures/overview-mantle.png}
\caption{This is Mantle.}
\end{figure}

>>>>

\paragraph*{Malacology:} Malacology exposes Ceph's PAXOS-based monitoring
service implementing a generic API
for adding arbitrary values to existing subsystem cluster maps, namely to the 
OSD map and the MDS map. As a consequence of this, applications can define 
simple but useful domain-specific logic to the PAXOS state machine, such as 
authorization control (just specific clients can write new values) or to trigger 
actions based on specific values (e.g. sanitize values). Since the monitor is 
intended to be out of high-performance I/O paths, a general guideline is to make 
use of this functionality infrequently and to assign small values to maps. 
Malacology itself makes use of this functionality to register, version and 
propagate dynamic code (Lua scripts) for new object interfaces defined in OSDs 
(\S\ref{active-storage}) and load balancing policies in MDSs 
(\S\ref{malacology:mds}).

@@

\begin{figure}[htbp]
\centering
\includegraphics{figures/implementation.png}
\caption{Malacology re-uses Ceph subsystems to allow users to dynamically define 
new object interfaces and load balancing policies. It achieves this by extending 
the OSD and MDS subsystems with an embedded Lua VM. To manage newly dynamic 
interface classes, it exposes the core functionality of the Monitor to allow 
arbitrary data to be associated to ODS and MDS cluster maps. After new 
interfaces are submitted to the monitor and the associated Paxos proposal is 
accepted by the monitor quorum, the script is redundantly and consistently 
distributed to OSDs so this snippets persist.
\label{fig:implementation}}
\end{figure}

@@
